% ====================================================================
\section{Simulation Requirements}
\label{sec:twinkles1:simulations}
% ====================================================================

\contact{Phil Marshall}{@drphilmarshall}

% --------------------------------------------------------------------

\subsection{\OpSim}

Enigma 1189.

No new functionality.

% --------------------------------------------------------------------

\subsection{\CatSim}

Requirement.  CatSim Labeling.
Added objects have labels that connect to input catalogs.  Reference catalog, instance catalog must have matching labels.
Validation:  Joins must be complete.  Objects labeled 'X' have to appear in the instance catalog labeled 'X'.

Requirement.  CatSim+SupernovaRealizer
Type Ia supernovae with SupernovaRealizer. 
Validation:  Double-check CatSim instance catalogs against output from SupernovaRealizer.

Requirement:  CatSim+Supernovae in ``realistic'' hosts 
Validation:  Check that the SN appears in the same place (RA, Dec) as written in the instance catalogs.
Validation:  Check the distribution of SN-host galaxy offsets.

Requirement:  CatSim Lens Sprinkler
Lensed quasars from TDC1 Gold Sample catalog (OM10 subset):
Realistic lens (massive elliptical) galaxies, placed in front of quasars.
Validation:  Double-check CatSim instance catalogs against output from OM10/Sprinkler

Requirement:  CatSim Time Delay
realistic AGN variability with requested parameters. Time delays.
No microlensing needed. Redshifts supplied in catalog.
Validation:  Step up from instance catalog.  Is the offset implemented correctly.
Validation:  Are instance catalog magnitudes not identical for set of images of the same quasar?


% --------------------------------------------------------------------

\subsection{\PhoSim}

No new functionality required.

% ====================================================================
